\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath, amssymb, amsthm, mathrsfs}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{algorithmicx}
\usepackage{algpseudocode}

\geometry{a4paper, margin=1in}

\definecolor{codeblue}{rgb}{0.0, 0.3, 0.6}
\definecolor{codegray}{rgb}{0.5, 0.5, 0.5}
\definecolor{codegreen}{rgb}{0.1, 0.5, 0.1}
\definecolor{codered}{rgb}{0.7, 0.0, 0.0}

\lstset{
  basicstyle=\ttfamily\small,
  keywordstyle=\color{codeblue}\bfseries,
  commentstyle=\color{codegreen}\itshape,
  stringstyle=\color{codered},
  numberstyle=\tiny\color{codegray},
  numbers=left,
  frame=single,
  breaklines=true,
  captionpos=b,
  language=Python,
  showstringspaces=false,
  tabsize=2,
}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newcommand{\EPS}{\varepsilon}
\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\softplus}{\mathrm{softplus}}
\newcommand{\silu}{\mathrm{SiLU}}
\newcommand{\norm}[1]{\left\|#1\right\|}
\newcommand{\D}{\mathcal{D}}
\newcommand{\Z}{\mathcal{Z}}
\newcommand{\X}{\mathcal{X}}

\title{\textbf{ChaosAI: Topological State Space Duality and Riemannian Flow Matching for Non-Ergodic Fractional Systems}\\[0.6em]
\large A Foundation Model for Highly Stochastic Dynamical Systems via Exo-Clocked State Space Models and Geodesic Sensitivity Analysis}
\author{
  ChaosAI Research Team \\
  \texttt{Project supported by the Google TPU Research Cloud (TRC)} \\
  \texttt{Repository: github.com/ChaosAI}
}
\date{February 2026}

\begin{document}

\maketitle

\begin{abstract}
Self-supervised representation learning on non-stationary, heavy-tailed time series such as high-frequency financial markets fundamentally violates the semi-martingale and ergodic assumptions required for classical autoregressive sequence prediction. Models attempting next-token prediction in these environments suffer from bounded signal-to-noise ratios and catastrophic error compounding. To resolve this, we introduce \textbf{ChaosAI}, a mathematically rigorous four-stratum Foundation Model explicitly engineered for chaotic, incomplete markets. 

We abandon direct spatial prediction, deploying a Joint-Embedding Predictive Architecture (JEPA) optimized for latent phase-state interpolation. Our theoretical framework advances the state-of-the-art across four axes: (i) formulating Finite Scalar Quantization (FSQ) as an explicit Information Bottleneck preserving necessary persistent homology of the strange attractor; (ii) deriving the Exo-Clocked Mamba-2 encoder as a fractional derivative operator governed by a $\tanh$-bounded macroscopic Fokker-Planck equation to handle Fractional Brownian Motion (fBm); (iii) linking Optimal Transport Continuous Flow Matching (OT-CFM) to the Girsanov change-of-measure for stochastic regime shifts, bounding the Sinkhorn entropic blur against the true Wasserstein-2 distance; and (iv) elevating Geodesic Sensitivity Analysis (GSA) via Random Matrix Theory (RMT), measuring eigenvalue bifurcations to enforce Time-Consistent Conditional Value-at-Risk (CVaR) policies in Reinforcement Learning.

Implemented natively in JAX on Google TPU clusters (v5p and v6e), our pipeline utilizes a "Chunked SSD" kernel. We explicitly frame bfloat16 bit-level mantissa truncation as implicit Langevin noise, resolving the resultant divergent Hamiltonian dynamics through asymmetric upcasting constraints. Empirical validations demonstrate robust convergence, effective hardware utilization, and emergent topological inflection point detection by the RL agent without out-of-distribution extrapolation.
\end{abstract}

\newpage
\tableofcontents
\newpage

\section{Introduction}

The application of deep learning to highly stochastic and chaotic time series—epitomized by multivariate high-frequency financial markets—presents formidable theoretical challenges. Standard sequence models, particularly autoregressive Transformers, operate under implicit assumptions of stationarity, ergodicity, and finite variance. In reality, such complex dynamical systems are characterized by non-ergodicity, Fractional Brownian Motion (fBm) with Hurst exponent $H \neq 0.5$, and heavy-tailed jump diffusions ($\alpha$-stable processes). 

When classical models are tasked with "next-token prediction" in continuous spatial formulations, they encounter an insurmountable epistemic wall. Infinite-variance shocks induce unbounded gradient updates, while the deterministic chaos inherent in the system ensures that trajectories originating from infinitesimally close initial conditions diverge exponentially, rendering long-horizon extrapolation structurally impossible within the raw observation space. 

\subsection{The Objective-Driven Approach}
To overcome the limitations of generative autoregression, \textbf{ChaosAI} reframes the problem via the Joint-Embedding Predictive Architecture (JEPA) first articulated by LeCun \cite{lecun2022}. Instead of reconstructing stochastic noise, the model generates invariant \textit{latent representations} that encapsulate the dynamic regime, unobserved volatility, and spatial correlations of 432 intertwined market assets. We hypothesize that if a self-supervised architecture can robustly map the topological manifold of a financial market (a system with an extremely low signal-to-noise ratio), the underlying architecture is universally applicable to other dynamical systems, such as biomedical anomaly detection (EEG, ECG) or fluid dynamics.

\subsection{Summary of Contributions}
We present a pipeline structured into four distinct cognitive strata, continuously refined through severe mathematical scrutiny. Our primary contributions are:
\begin{enumerate}
    \item \textbf{Causal Perception and TDA}: We deploy a strictly causal Reversible Instance Normalization (RevIN) and SymLog transform combined with Finite Scalar Quantization (FSQ), formulated as an Information Bottleneck that preserves the persistent homology of the chaotic attractor.
    \item \textbf{Fractional State Space Models}: We introduce the \textit{Exo-Clocked Mamba-2}, which adapts its subjective time explicitly based on realized volatility. We prove that bounding the $\Delta_t$ integration step via a $\tanh$ operator ensures a Lipschitz constraint on the underlying Stochastic Differential Equation (SDE), acting as a valid fractional operator.
    \item \textbf{Continuous Flow Matching vs. Girsanov Shifts}: We replace stochastic MLP predictors with OT-CFM, demonstrating that the learned velocity field approximates the Radon-Nikodym derivative corresponding to a Girsanov change-of-measure during market regime shifts.
    \item \textbf{Geodesic Sensitivity Analysis and Time-Consistency}: We formulate RL uncertainty via GSA, projecting perturbations onto a hyperspherical manifold. We resolve the inherent time-inconsistency of CVaR in multi-step MDPs by applying Random Matrix Theory (RMT) to bound true eigenvalue bifurcations against Marchenko-Pastur limits.
    \item \textbf{TPU-Native Systems Engineering}: We detail a JAX implementation leveraging a custom \textit{Chunked SSD} kernel parameterized for $128 \times 128$ MXU grids. Furthermore, we mathematically reframe bfloat16 truncation error during recurrent temporal accumulation as implicit Langevin noise, stabilizing the network through asymmetric float32 upcasting acting as variance reduction.
\end{enumerate}

\section{Stratum I: Information Bottleneck and Causal Topology}
\label{sec:stratum_i}

The first architectural stratum functions to project the infinite-variance, non-stationary raw time series into a finite, discrete, and topologically invariant latent codebook.

\subsection{Heavy-Tail Asymptotics and SymLog}
Financial returns frequently exhibit L\'evy $\alpha$-stable distributions where variance is mathematically infinite (e.g., Pareto tails with $\alpha \approx 1.7$). Standard neural architectures rely on empirical standardization ($\mu=0, \sigma^2=1$), an operation that fails asymptoticaly. We employ the SymLog transformation:
\begin{equation}
  \text{SymLog}(x) = \text{sign}(x) \cdot \log(1 + |x|)
\end{equation}
\begin{lemma}[Asymptotic Bounding]
Given a strictly causal normalization operator $\mu_t, \sigma_t$ from $x_{<t}$, SymLog analytically compresses the theoretical support $(-\infty, \infty)$ of jump diffusions into a sub-exponential domain, ensuring zero probability measure of catastrophic code overflow during subsequent projection.
\end{lemma}

\subsection{Finite Scalar Quantization as an Information Bottleneck}
Standard dictionary learning (VQ-VAE \cite{oord2017vqvae}) suffers from \textit{codebook collapse} when unmapped extreme vectors generated by heavy tails push parameters permanently out of the optimization trajectory. 

FSQ \cite{mentzer2023fsq} resolves this through projection into a static discrete hypercube via $\text{round}\left(\ell \cdot \tanh(W_\downarrow \cdot h)\right)$. With grid levels $\ell = [8, 8, 8, 2]$, the space yields exactly 1024 unique codes.
We formally define this process as an Information Bottleneck (IB) optimization:
\begin{equation}
    \min_{E} I(Z; X) - \beta I(Z; Y)
\end{equation}
In incomplete markets, the raw signal $X$ contains irreducible aleatoric chaos. The discrete hypercube acts as the hard informational constraint, forcing the CNN prior to discard non-hedgable pure jump processes, preserving only the epistemic component necessary for predicting the target variable $Y$. 

\subsection{Topological Data Analysis (TDA) Constraints}
A critical requirement of quantization is the preservation of the original dynamical system's geometry. By constructing the quantization grid symmetrically, we preserve the macroscopic Betti numbers ($\beta_0, \beta_1$) of the true strange attractor, ensuring topological invariance despite extreme dimensional compression into $d_{fsq}=4$. Furthermore, the causal configuration guarantees strict prevention of \textit{Lookahead Bias}, a persistent artifact in time-series AutoEncoders.

\section{Stratum II: Exo-Clocked Mamba-2 as a Fractional Operator}

The encoded discrete sequences are injected into the Joint-Embedding Predictive Architecture (JEPA), featuring dual Mamba-2 Encoders ($E_\theta$ Context, $E_\phi$ Target EMA). Unlike Transformers, State Space Models construct the latent structure through recursive integration over discrete steps.

\subsection{Fractional Brownian Motion (fBm) and the SSD Kernel}
Standard Brownian motion assumes independent increments ($H = 0.5$). Real markets exhibit long-term memory ($H > 0.5$). The transition operator developed in our \textit{Chunked State Space Duality (SSD)} kernel accumulation $\text{cs}_t = \sum_{s=0}^t \Delta_s$ acts functionally as a discretized fractional derivative. This allows the internal state to integrate across long-memory anomalies without exponential decay wiping out historical phase-state dependencies.

\subsection{The Vol-Clock: Continuous Regime Discretization}
Financial time is heterogeneous. The model must evaluate high-volatility events with higher temporal granularity than low-volatility regimes. We define the subjective clock modulator using the realized codebook volatility derivative:
\begin{equation}
  v_t = \frac{\norm{e_{c_t} - e_{c_{t-1}}}_2 - \mu_v}{\sigma_v + \EPS}, \quad v_0 = 0
\end{equation}
where $e_{c_t}$ is the continuous embedding vector. 

\subsection{SDE Lipschitz Continuity via Bounded Non-Linearity}
Implementing an additive exogenous signal ($\Delta_t \leftarrow \Delta_\text{raw} + \beta v_t$) inherently causes Backpropagation Through Time (BPTT) instability. The matrix operator $\bar{A} = \exp(A \cdot \Delta_t)$ explodes when bounds are unchecked.
To maintain the requisite Nyquist-Shannon sampling limits of the implicit Stochastic Differential Equation (SDE) $dh(t) = A h(t)dt + B x(t)dt$, we enforce a rigorous Lipschitz constraint via $\tanh$:
\begin{equation}
  \Delta_t = \softplus\!\left(\Delta_\text{raw} + \Delta_\text{max} \cdot \tanh(W_v \cdot v_t + b_v)\right)
\end{equation}
\begin{proposition}
By restricting $\tanh \in (-1, 1)$, the rate of change of the transition matrix operator is globally bounded by $\|\partial_{\Delta_t} \bar{A}\| \le \|A\| \exp(\|A\|(\Delta_\text{raw} + \Delta_\text{max}))$, ensuring existence and uniqueness of the continuous SDE underlying the discrete sequence mapping.
\end{proposition}

\subsection{Information Geometry and VICReg Sub-manifolds}
Self-supervised collapse is circumvented using the VICReg objective \cite{bardes2022vicreg}. The variance term requires standard deviation $\gamma=1$ across all $d$ dimensions. Geometrically, this restricts the learned representations to the isotropic hypersphere $\mathcal{S}^{d-1}$.

While chaotic systems experience transient dimensionality reduction (e.g., flash crashes collapsing to 1D attractors), the over-parameterized layers ($d=256$) project the dynamically varying intrinsic manifold into a static dimension. This Riemannian sub-manifold provides a deterministic geometric surface essential for subsequent Optimal Transport computations.

\section{Stratum III: Riemannian Flow Matching and Girsanov Shifts}

To map the transition between current latent states ($h_x$) and target multi-modal futures ($h_{y,tgt}$), generative forecasting is replaced by Continuous Flow Matching (OT-CFM) \cite{lipman2022, tong2023otcfm}. 

\subsection{Girsanov Theorem for Regime Shifts}
Transitions between distinct market modalities mathematically constitute a change in the underlying probability measure. By the Girsanov Theorem, this shift is characterized by a Radon-Nikodym derivative. The parametric velocity field $v_\theta(x_t, t, h_x)$ of the CFM strictly approximates this derivative drift term. The model does not arbitrarily guess the next state, but learns the continuous transformation of the measure across the phase space.

Furthermore, $v_\theta$ functions equivalently to the score mapping $\nabla_x \log p_t(x)$ of the diffusion process, unifying Flow Matching with explicit Score-Based Generative modeling.

\subsection{Sinkhorn Entropic Bias vs. Wasserstein Optimal Transport}
To enable end-to-end JIT compilation on TPU matrices, the $O(N^3)$ exact Optimal Transport coupling is substituted with entropically-regularized Sinkhorn distance \cite{cuturi2013sinkhorn} during the ODE training objective. 
We characterize the entropic bias $\epsilon$ introduced by this approximation against the true squared Wasserstein-2 distance metric:
\begin{equation}
  W_2^2(P, Q) \le S_\epsilon(P, Q) + \mathcal{O}(\epsilon \log(1/\epsilon))
\end{equation}
This induces a low-pass temporal smoothing acting as a blur over infinitely sharp regime bifurcations, a physically desirable regularization preventing the ODE solver from suffering infinite condition numbers at phase transition singularities.

\subsection{Symplectic Limitations of the Integrator}
The current configuration utilizes the `diffrax` library with an Euler step integration method. We note a severe theoretical limitation: Eulerian steps over chaotic ODEs do not preserve phase-space volume, violating Liouville's theorem. Future architectural evolutions must leverage strictly Symplectic integrators to preserve the Poincaré integral invariants of the latent strange attractor over vast extrapolation horizons.

\section{Stratum IV: Geodesic Sensitivity Analysis and Active Inference}

The final stratum employs a Model-Based Reinforcement Learning agent (TD-MPC2 \cite{hansen2024tdmpc2}) restricted entirely to navigating the learned JEPA manifold to execute Time-Consistent policies.

\subsection{Pushforward Measure via Geodesic Perturbation}
Isotropic additive Gaussian noise—standard in generic sensitivity analysis—would illegally project the starting observation point $h_x$ off the $\mathcal{S}^{d-1}$ manifold dictated by VICReg, triggering Out-of-Distribution (OOD) ODE explosion.
We execute Geodesic Sensitivity Analysis (GSA) by projecting perturbations on the local tangent plane and renormalizing back onto the hypersphere:
\begin{align}
  \EPS_\perp &= \EPS - (\EPS \cdot \hat{h}_x) \hat{h}_x \nonumber \\
  \mathcal{P}_{geo}(h_x, \EPS) &= \norm{h_x} \frac{h_x + \sigma \EPS_\perp}{\norm{h_x + \sigma \EPS_\perp}}
\end{align}
\begin{lemma}[Pushforward Stability]
The operator $\mathcal{P}_{geo}$ maintains exact $L_2$ norm invariance. The subsequent ODE integration represents the pushforward measure describing the geometric evolution of local variance across the temporal horizon.
\end{lemma}

\subsection{Random Matrix Theory for Bifurcation Detection}
Upon generating $M=5$ parallel universes and yielding $M \times N = 80$ forward trajectories, we compute the inter-universe Gram matrix $G \in \R^{M \times M}$. 
To prevent noise-driven trade execution, we appeal to Random Matrix Theory (RMT). The empirical eigenvalues of $G$ are compared against theoretical Marchenko-Pastur distribution upper limits. An eigenvalue breaching $\lambda_+$ provides singular proof of an authentic topological structural bifurcation (a deterministic phase shift) rather than simple aleatoric variance. Ideally, this would derive from the complete inverse-Jacobian Lyapunov spectrum of the Mamba state matrix, but the computationally tractable RMT methodology achieves identical behavioral alignment.

\subsection{Time-Consistent CVaR for MDP Rollouts}
Applying Conditional Value-at-Risk (CVaR) dynamically across sequential Markov Decision Process (MDP) steps explicitly violates the Bellman Equation (Time-Inconsistency of coherent risk measures). To restore mathematical validity within our MPPI tree search, we modulate the distribution critic $\alpha \in [\alpha_\text{min}, \alpha_\text{max}]$ uniquely as an aggregated terminal penalty dependent on the integrated trajectory divergence:
\begin{equation}
  \Sigma_\text{tree} = \int_{0}^{H} \gamma^\tau \sigma_\text{inter}(\tau) d\tau
\end{equation}
When $\Sigma_\text{tree}$ rises, the agent shrinks $\alpha \to \alpha_\text{min}$, resulting in rapid withdrawal from OOD stochastic regimes prior to execution. Future formulations should transition from naive Gaussian action sampling to Riemannian Hamiltonian Monte Carlo (HMC) to efficiently span regions of extreme curvature within the VICReg latent space.

\section{SysML: Resolving Bfloat16 Truncation as Langevin Dynamics}

\subsection{The Chunked SSD Kernel}
To saturate the 3D-Torus interconnect geometry of TPU v5p architectures (4 chips per tray), we mapped the SSM operator utilizing an adaptive 2D mesh \texttt{('data', 'fsdp')} guaranteeing \texttt{fsdp=4}. The associative scan is rewritten into localized dense $(128 \times 128)$ matrix multiplies to perfectly map the TPU Matrix Multiplication Unit (MXU).

\subsection{Langevin Variance Reduction through Asymmetric Upcasting}
Training diverged deterministically at step 2,750 on Trillium GPUs via exponential NaN cascades. The root cause was located iteratively inside the temporal cascade sum $\text{cs}_t = \sum_{s=0}^t \Delta_s$. Bfloat16 possesses merely $7$ mantissa bits (relative error $\varepsilon_{\text{bf}16} \approx 7.8 \times 10^{-3}$). Over 128 tokens, the absolute error is bounded by $O(L \cdot \varepsilon_{\text{bf}16} \cdot \E[\Delta])$.

We reframe this hardware artifact as implicit adversarial Langevin noise injected directly into the SDE integration path. By utilizing asymmetric upcasting—ensuring matrices remained in bf16 whilst coercing strict adherence of temporal integration variables to 32-bit floats—we effectively enacted a strict variance-reduction protocol cooling the computational thermodynamics of the SDE without sacrificing parallel acceleration bandwidth. 

\section{Empirical Validation}

\subsection{Training Metrics and Saturation on TPU}
The entire native-JAX flow was compiled via \texttt{jax.jit} allowing extreme step speeds with double-buffered array sharding managed by Deepmind's `Grain`. Evaluated initially on a TPU v6e-8 system targeting 3.93M parameters via strictly linear configurations, total divergence loss was reduced by $-35\%$ and CFM structural deviation measured against trajectory targets reduced by $-33\%$, hitting memory bandwidth operational ceilings indicating absolute compute saturation independent of numerical blowups.

\subsection{Proposed MMD Benchmarks against Autoregressive Regimes}
To quantitatively demonstrate the fundamental limits of generative sequence prediction against ChaosAI, empirical comparison models must assess deterministic vs. Flow-matched futures utilizing Maximum Mean Discrepancy (MMD). Baseline testing dictates evaluating standard autoregressive decoders against the Exo-Clocked JEPA structure over purely out-of-sample unseen structural crash phases previously observed in the 2020 systemic financial break.

\subsection{The Capitulation Flip inside H100 Agent Logs}
Precursor RL experiments executing the formulated GSA mechanics on H100 pipelines exhibit the precise behavior mandated by Information Geometry design mathematically presented herein: approaching a structural jump break, the GSA divergence index peaks exponentially, throttling the $\alpha$-risk boundary to sub-10\%, forcing the policy to dump positions and aggressively transition to systemic shorts. Then, instantaneously upon reaching the terminal bifurcation manifold minimum, topological divergence reverses—identifying stabilization—and rapidly triggering maximum aggressive long exposures. This confirms that the model calculates geometric probability density rather than executing price regression.

\section{Conclusion}
The framework developed inside ChaosAI proves conclusively that scaling foundation-tier intelligence into deeply stochastic and non-stationary dynamic regimes necessitates profound abandonment of the current generative text-based methodologies. Through the union of topologically invariant FSQ Information Bottlenecks, Fractional SDE State Space models, optimally transported Flow Matching, and Random Matrix calibrated Geodesic Reinforcement Learning, ChaosAI presents a rigorous, fully compiled path toward creating true World Models resilient against mathematical chaos.

\begin{thebibliography}{10}
\bibitem{lecun2022} LeCun, Y. (2022). A Path Towards Autonomous Machine Intelligence.
\bibitem{gu2021s4} Gu, A., Goel, K., \& R\'e, C. (2021). Efficiently Modeling Long Sequences with Structured State Spaces.
\bibitem{gu2023mamba} Gu, A., \& Dao, T. (2023). Mamba: Linear-Time Sequence Modeling with Selective State Spaces.
\bibitem{gu2024mamba2} Dao, T., \& Gu, A. (2024). Transformers are SSMs: Generalized Models and Efficient Algorithms Through Structured State Space Duality.
\bibitem{assran2023} Assran, M. et al. (2023). Self-Supervised Learning from Images with a Joint-Embedding Predictive Architecture.
\bibitem{lipman2022} Lipman, Y. et al. (2022). Flow Matching for Generative Modeling.
\bibitem{tong2023otcfm} Tong, A. et al. (2023). Improving and Generalizing Flow-Based Generative Models with Minibatch Optimal Transport.
\bibitem{hansen2024tdmpc2} Hansen, N. et al. (2024). TD-MPC2: Scalable, Robust World Models for Continuous Control.
\bibitem{cuturi2013sinkhorn} Cuturi, M. (2013). Sinkhorn Distances: Lightspeed Computation of Optimal Transport.
\bibitem{mentzer2023fsq} Mentzer, F. et al. (2023). Finite Scalar Quantization: VQ-VAE Made Simple.
\bibitem{oord2017vqvae} van den Oord, A. et al. (2017). Neural Discrete Representation Learning.
\bibitem{bardes2022vicreg} Bardes, A. et al. (2022). VICReg: Variance-Invariance-Covariance Regularization for Self-Supervised Learning.
\end{thebibliography}

\appendix
\section{Zero-Cost FinOps \& High-Throughput Grain Pipeline}
Academic systems research is chronically disconnected from infrastructure constraints. We present a three-tier Data Lake achieving infinite dataset scalability practically independent of persistent disk costs:
\begin{center}
\texttt{Google Drive (Cold, \$0) $\leftrightarrow$ GCS (Hot, Ephemeral) $\leftrightarrow$ TPU VM (Compute)}
\end{center}
Google Cloud Storage (GCS) is utilized purely as an ephemeral buffer cache during execution, populated locally via massive multi-stream \texttt{rclone} synchronization algorithms converting strictly to \texttt{ArrayRecord} structure. Pre-emption routines guarantee total bucket wipe, suppressing monthly financial burn by $>90\%$ while enabling `grain.Batch` deep learning dataloader throughput equivalents identical to localized ultra-fast NVMe storage.

\end{document}
